Integration of national demographic-disturbance relationships and local data can improve caribou population viability projections and inform monitoring decisions

### 2025-02-24 analysis/paper/supplement.Rmd
submitted.

# (APPENDIX) Supplementary Material for Integration of national demographic-disturbance relationships into local caribou population viability projections can reduce uncertainty and inform monitoring decisions {-}

>>>>

# (APPENDIX) Supplementary Material for Integration of national demographic-disturbance relationships and local data can improve caribou population viability projections and inform monitoring decisions {-}
